Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-14 paper/paper.qmd
Update paper.qmd

# Experiment

@@

@@

@@

## Divergent Effects on Male vs. Female Entrepreneurs 
For the male participants in our study, the impact of various form of capital assistance displays the same complex pattern across different business outcomes. The likelihood of owning a business does not significantly change with the introduction of Micro Credit, In-Kind Grant, or Cash Grant, it’s evident by the negligible coefficients. However, positive performances are shown on the New Asset, with the latter showing a slightly larger effect on In-Kind Grant. Monthly Expenditure decreases significantly with all forms of capital assistance, which may indicate more efficient business operations or a reduction in business size or activity, which is similar with that of female participants. In terms of Monthly Revenue, we observed a decline with Micro Credit and a more obvious decline with Cash Grants, but there is only slight change with In-Kind Grants. Lastly, Monthly Profit does not show notable improvement with the capital assistance provided, although there is a insignificant trend towards reduced profits, particularly with Micro Credit and Cash Grants.

@@

@@

Before we study the differential impact of financial support on Business Outcomes across genders, Income Outcomes is also a crucial for researching effective economic empowerment programs. Table 3 offers insight into gender-specific outcomes of three financial supports on income. The data can be analyzed to compare the influence affecting labor income and total income for female and male participants. For female participants, Both Cash Grant and In-Kind Grant appear to have the significant positive effect on both labor and total income, with more substantial effect by providing Cash Grant. Micro Credit, while showing a positive in labor income but converse effect on total income. On the male side, the effects of financial supports are less clear, with Micro Credit and In-Kind Grant associated with decrease in labor income and no clear pattern in total income. However, Cash Grant show a slight positive effect on labor income but a decrease in total income. 
If we compare the gender-specific effect, it seems that women benefit more from financial supports in terms of income outcomes. This aligns with the idea that women may perform between than men with these types of financial support when it comes to income outcomes.

>>>>

# Experiment 
// TODO: Table 1: Baseline Balance of Variables Across Treatment Status

@@

// TODO: Impacts fof Financial Supports on Business Outcomes

@@

//TODO: Table 3.1:  Impacts of Financial Supports on Business Outcomes Among Female Participants

@@

//TODO: Table 3.2: Impacts of Financial Supports on Business Outcomes Among Male Participants
For the male participants in our study, the impact of various form of capital assistance displays the same complex pattern across different business outcomes. The likelihood of owning a business does not significantly change with the introduction of Micro Credit, In-Kind Grant, or Cash Grant, it’s evident by the negligible coefficients. However, positive performances are shown on the New Asset, with the latter showing a slightly larger effect on In-Kind Grant. Monthly Expenditure decreases significantly with all forms of capital assistance, which may indicate more efficient business operations or a reduction in business size or activity, which is similar with that of female participants. In terms of Monthly Revenue, we observed a decline with Micro Credit and a more obvious decline with Cash Grants, but there is only slight change with In-Kind Grants. Lastly, Monthly Profit does not show notable improvement with the capital assistance provided, although there is a insignificant trend towards reduced profits, particularly with Micro Credit and Cash Grants.

## Divergent Effects on Male vs. Female Entrepreneurs

//TODO: Figure 1: Female Monthly Profit vs. Male Monthly Profit

@@

//TODO: Figure 1.2: Female New Asset vs. Male New Asset

@@

//TODO: Table 4.1: Impacts of Financial Supports on Income Outcomes Among Female Participants

//TODO: Table 4.2: Impacts of Financial Supports on Income Outcomes Among Male Participants

Before we study the differential impact of financial support on Business Outcomes across genders, Income Outcomes is also a crucial for researching effective economic empowerment programs. Table 4.1 and Table 4.2 offers insight into gender-specific outcomes of three financial supports on income. The data can be analyzed to compare the influence affecting labor income and total income for female and male participants. For female participants, Both Cash Grant and In-Kind Grant appear to have the significant positive effect on both labor and total income, with more substantial effect by providing Cash Grant. Micro Credit, while showing a positive in labor income but converse effect on total income. On the male side, the effects of financial supports are less clear, with Micro Credit and In-Kind Grant associated with decrease in labor income and no clear pattern in total income. However, Cash Grant show a slight positive effect on labor income but a decrease in total income. 
If we compare the gender-specific effect, it seems that women benefit more from financial supports in terms of income outcomes. This aligns with the idea that women may perform between than men with these types of financial support when it comes to income outcomes.
